Inferring true changes in microbial abundance from taxonomically-biased microbiome measurements

### 2021-11-09 abundance-measurement.Rmd
Fix figure rendering in pdf output
The calls to `knitr::include_graphics()` were failing in pdf output
because these calls have to be included in a top level R statement. This
commit fixes this issue; it also removes code redundancy, switches to
relative paths (the recommended method for bookdown), and puts the pdf
images in a new folder contained within the project directoty.

```{r error-proportions, out.width = '90%', fig.cap = '(ref:cap-error-proportions)', cache = TRUE}
svg_path <- here("figures/illustrations/error-proportions.svg")
if (knitr::is_html_output()) {
  knitr::include_graphics(svg_path)
} else if (knitr::is_latex_output()) {
  # cowplot::ggdraw() + cowplot::draw_image(svg_path)
  pdf_path <- file.path("/tmp", "bookdown-differential-abundance-theory",
    "error-proportions.pdf")
  args <- c(
    "--export-area-page", 
    "--export-type=pdf", 
    str_c("--export-filename=", pdf_path),
    svg_path
  )
  system2("inkscape", args = args)
  knitr::include_graphics(pdf_path)
  rm(pdf_path)
}
rm(svg_path)
```

>>>>

```{r error-proportions, out.width = '90%', fig.cap = '(ref:cap-error-proportions)', cache = TRUE}
svg_path <- "figures/illustrations/error-proportions.svg"
if (knitr::is_html_output()) {
  fig_path <- svg_path
} else if (knitr::is_latex_output()) {
  fig_path <- svg_to_pdf(svg_path)
}
knitr::include_graphics(fig_path)
rm(svg_path, fig_path)
```

### 2021-11-09 differential-abundance.Rmd
Fix figure rendering in pdf output
The calls to `knitr::include_graphics()` were failing in pdf output
because these calls have to be included in a top level R statement. This
commit fixes this issue; it also removes code redundancy, switches to
relative paths (the recommended method for bookdown), and puts the pdf
images in a new folder contained within the project directoty.

```{r regression-example, fig.cap = '(ref:regression-example)'}
svg_path <- here::here(
  "notebook/_posts/2021-08-03-simulate-regression-example/",
  "simulate-regression-example_files/figure-html5",
  "main-figure-1.svg"
)
if (knitr::is_html_output()) {
  knitr::include_graphics(svg_path)
} else if (knitr::is_latex_output()) {
  # cowplot::ggdraw() + cowplot::draw_image(svg_path)
  pdf_path <- file.path("/tmp", "bookdown-differential-abundance-theory",
    "regression-example.pdf")
  args <- c(
    "--export-area-page", 
    "--export-type=pdf", 
    str_c("--export-filename=", pdf_path),
    svg_path
  )
  system2("inkscape", args = args)
  knitr::include_graphics(pdf_path)
  rm(pdf_path)
}
rm(svg_path)
```

>>>>

```{r regression-example, fig.cap = '(ref:regression-example)'}
svg_path <- here::here(
  "notebook/_posts/2021-08-03-simulate-regression-example/",
  "simulate-regression-example_files/figure-html5",
  "main-figure-1.svg"
)
if (knitr::is_html_output()) {
  fig_path <- svg_path
} else if (knitr::is_latex_output()) {
  fig_path <- svg_to_pdf(svg_path)
}
knitr::include_graphics(fig_path)
rm(svg_path, fig_path)
```

### 2021-11-09 introduction.Rmd
Fix figure rendering in pdf output
The calls to `knitr::include_graphics()` were failing in pdf output
because these calls have to be included in a top level R statement. This
commit fixes this issue; it also removes code redundancy, switches to
relative paths (the recommended method for bookdown), and puts the pdf
images in a new folder contained within the project directoty.

```{r basic-problem, fig.cap = '(ref:cap-basic-problem)'}
svg_path <- here::here(
  "notebook/_posts/2021-10-27-illustrate-the-problem/illustrate-the-problem_files", "figure-html5/brooks_lcrisp_prop_and_fc-1.svg"
)
if (knitr::is_html_output()) {
  knitr::include_graphics(svg_path)
} else if (knitr::is_latex_output()) {
  # cowplot::ggdraw() + cowplot::draw_image(svg_path)
  pdf_path <- file.path("/tmp", "bookdown-differential-abundance-theory",
    "error-proportions.pdf")
  args <- c(
    "--export-area-page", 
    "--export-type=pdf", 
    str_c("--export-filename=", pdf_path),
    svg_path
  )
  system2("inkscape", args = args)
  knitr::include_graphics(pdf_path)
  rm(pdf_path)
}
rm(svg_path)
```

>>>>

```{r basic-problem, fig.cap = '(ref:cap-basic-problem)'}
# NOTE: call to include_graphics() has to be in top level expression
svg_path <- fs::path(
  "notebook/_posts/2021-10-27-illustrate-the-problem/illustrate-the-problem_files", 
  "figure-html5/brooks_lcrisp_prop_and_fc-1.svg"
)
if (knitr::is_html_output()) {
  fig_path <- svg_path
} else if (knitr::is_latex_output()) {
  fig_path <- svg_to_pdf(svg_path)
}
knitr::include_graphics(fig_path)
rm(svg_path, fig_path)
```

### 2021-11-09 solutions.Rmd
Fix figure rendering in pdf output
The calls to `knitr::include_graphics()` were failing in pdf output
because these calls have to be included in a top level R statement. This
commit fixes this issue; it also removes code redundancy, switches to
relative paths (the recommended method for bookdown), and puts the pdf
images in a new folder contained within the project directoty.

```{r calibration-example, fig.cap = '(ref:cap-calibration-example)'}
fig_path <- here::here(
  "notebook/_posts/2021-10-25-brooks2015thet-calibration",
  "brooks2015thet-calibration_files/figure-html5/brooks2015thet_fc_calibration-1.png"
)
knitr::include_graphics(fig_path)
rm(fig_path)
```

@@

```{r sensitivity-example, fig.cap = '(ref:cap-sensitivity-example)'}
svg_path <- here::here(
  "notebook/_posts/2021-10-18-evaluate-robustness-example/",
  "evaluate-robustness-example_files/figure-html5/summary_plot-1.svg"
)
if (knitr::is_html_output()) {
  knitr::include_graphics(svg_path)
} else if (knitr::is_latex_output()) {
  # cowplot::ggdraw() + cowplot::draw_image(svg_path)
  pdf_path <- file.path("/tmp", "bookdown-differential-abundance-theory",
    "sensitivity-example.pdf")
  args <- c(
    "--export-area-page", 
    "--export-type=pdf", 
    str_c("--export-filename=", pdf_path),
    svg_path
  )
  system2("inkscape", args = args)
  knitr::include_graphics(pdf_path)
  rm(pdf_path)
}
rm(svg_path)
```

>>>>

```{r calibration-example, fig.cap = '(ref:cap-calibration-example)', out.width = '100%'}
fig_path <- fs::path(
  "notebook/_posts/2021-10-25-brooks2015thet-calibration",
  "brooks2015thet-calibration_files/figure-html5/brooks2015thet_fc_calibration-1.png"
)
knitr::include_graphics(fig_path)
rm(fig_path)
```

@@

```{r sensitivity-example, fig.cap = '(ref:cap-sensitivity-example)'}
svg_path <- here::here(
  "notebook/_posts/2021-10-18-evaluate-robustness-example/",
  "evaluate-robustness-example_files/figure-html5/summary_plot-1.svg"
)
if (knitr::is_html_output()) {
  fig_path <- svg_path
} else if (knitr::is_latex_output()) {
  fig_path <- svg_to_pdf(svg_path)
}
knitr::include_graphics(fig_path)
rm(svg_path, fig_path)
```
